---
title: "PPT_with_officer_ex"
author: "Arush Mohan"
format: html
editor: visual
---

## Setup

```{r}
#| include=FALSE


knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(ggrepel)
library(lubridate)
library(readxl)
library(officer)
library(gt)

# Reading in the data from an excel file
data <- read_excel("data/DID_data_22-24.xlsx")

# Ingesting the ppt template with ICS branding

template_presentation <- read_pptx('input/template.pptx') 

```

## PPT Reference Layout

```{r}


layouts <- layout_summary(template_presentation)

print_placeholders <- function(layout_name, master_name){
  placeholders <- layout_properties(template_presentation, layout = layout_name, master = master_name)
  print(paste("PLaceholders:", layout_name, master_name))
  print(placeholders)
}

layout_properties(template_presentation, layout = "mod_layout_1", master = "Content Slide White")

walk2(.x = layouts$layout, .y = layouts$master, ~print_placeholders(.x, .y))

```

## Data Wrangling

```{r}

# In this example, the data has already been cleaned and organised in a 'tidy' format. 


# Modify the column names
data <- data %>%
  rename_all(~ tolower(gsub(" ", "_", .)))

```

## Building the PPT

### SLIDE 1: Add a title slide

```{r}

Presentation <- template_presentation %>%
  add_slide(layout = "No Image_Date/name multiple lines", master = "Presentation Title Slides") %>%
  ph_with(my_pres, value = "Presentation Building Workshop", location = ph_location_type(type = "title"))
```

### SLIDE 2: Adding the context section slide

```{r}

# Adding a section title slide

Presentation <- template_presentation %>%
  add_slide(layout = "Style 1", master = "Section Slide") %>%
  ph_with(my_pres, value = "Context", location = ph_location_label(ph_label = "Text Placeholder 6"))

```

### SLIDE 3: Adding Context

```{r}
# Adding the context slide with content

Presentation <- template_presentation %>%
  add_slide(layout = "One Column", master = "Content Slide White") %>%
  ph_with(value = "Context", location = ph_location_label(ph_label = "Title 1")) %>% 
  ph_with(value = block_list(
  fpar(ftext("Introduction to officer", prop = fp_text(bold = TRUE))),
  fpar(ftext("Creating Slides", prop = fp_text())),
  fpar(ftext("Adding Content", prop = fp_text(italic = TRUE)))
), location = ph_location_label(ph_label = "Content Placeholder 2"))

```

## Visualisations

### SLIDE 4: Modalities

```{r}

# Make a column chart that shows activity distribution by modality


plot <- ggplot(data, aes(x = modality)) +
  geom_bar(fill = "#005EB8") +
  labs(title = "Distribution of Modalities", x = "Modality", y = "Activity")+
  theme_nclicb()

# Add it to a slide
Presentation <- Presentation %>%
  add_slide(layout = "One Column", master = "Content Slide White")  %>%
  ph_with(value = "Activity Distribution by modality", location = ph_location_type(type = "title")) %>% 
  ph_with(value = plot, location = ph_location_label(ph_label = "Content Placeholder 2"))

```

### Summary table

```{r}
#| include=FALSE

# create a summary table showing the average IMD by modality

summary_data <- data %>%
  group_by(modality) %>%
  summarize(avg_imd_rank = mean(as.numeric(imd_rank_decile), na.rm = TRUE))


```

### MSK vs Non - MSK proportion

```{r}

# create a bar chart comparing the msk vs non- msk activity



# Add it a slide

```

### Boxplot imd rank deciles by modalites

```{r}
# Create a boxplot showing the IMD rank by modality




# Add it to the slide. Use a two column slide 


```

### Average IMD Rank Decile by Modality and MSK Flag

```{r}
# Create a summary table for avgerage IMD rank by modality and msk flag




# Create a gt table using the summary table 


# Save the gt table as an image 


# Add the table to the same slide as the previous one


```

### CCG Activity

```{r}
# Total activity per CCG


# Add it to a slide. Also add some commentary to the same slide


```

### Activity trend over time by modality - 2023-24

```{r}

# First, filter and aggregate the data by Year, Month, and Modality to count activities



# Plot the line chart with the date on the x-axis. Hint: you will need to use facet_wrap here



# Add the chart to a slide 

  
```

### Focusing on a subset -

```{r}
# Filter data for people aged 60+, group by year and modality


# Create a summary table using gt



# Save the table as an image


# Add it to a slide

```

### Heatmaps with crosstabs

```{r}

#Aggregate the data by modality and msk_flag



# Plot the heatmap



# Add it to a slide

```

## Creating the ppt output

```{r}

# Create the presentation as an output

Presentation %>%
  print(target = paste0('output/PPT_workshop.pptx'))

```
