---
title: "PPT_with_officer"
author: "Arush Mohan"
date: "`r Sys.Date()`"
output: html_document
---


## Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(ggrepel)
library(lubridate)
library(readxl)
library(officer)
library(gt)

# Reading in the data from an excel file
data <- read_excel("data/DID_data_22-24.xlsx")

# Ingesting the ppt template with ICS branding

template_presentation <- read_pptx('input/template.pptx') 

```



## Data Wrangling
```{r}

# In this example, the data has already been cleaned and organised in a 'tidy' format. 


# Modify the column names
data <- data %>%
  rename_all(~ tolower(gsub(" ", "_", .)))

```


## Building the PPT


### SLIDE 1: Add a title slide


```{r}

Presentation <- template_presentation %>%
  add_slide(layout = "No Image_Date/name multiple lines", master = "Presentation Title Slides") %>%
  ph_with(my_pres, value = "Presentation Building Workshop", location = ph_location_type(type = "title"))
```



### SLIDE 2: Adding the context section slide


```{r}

# Adding a section title slide

Presentation <- template_presentation %>%
  add_slide(layout = "Style 1", master = "Section Slide") %>%
  ph_with(my_pres, value = "Context", location = ph_location_label(ph_label = "Text Placeholder 6"))

```


### SLIDE 3: Adding Context

```{r}
# Adding the context slide with content

Presentation <- template_presentation %>%
  add_slide(layout = "One Column", master = "Content Slide White") %>%
  ph_with(value = "Context", location = ph_location_label(ph_label = "Title 1")) %>% 
  ph_with(value = block_list(
  fpar(ftext("Introduction to officer", prop = fp_text(bold = TRUE))),
  fpar(ftext("Creating Slides", prop = fp_text())),
  fpar(ftext("Adding Content", prop = fp_text(italic = TRUE)))
), location = ph_location_label(ph_label = "Content Placeholder 2"))

```


## Visualisations

### SLIDE 4: Modalities


```{r}

# Make a column chart that shows activity distribution by modality

plot <- ggplot(data, aes(x = modality)) +
  geom_bar(fill = "#005EB8") +
  labs(title = "Distribution of Modalities", x = "Modality", y = "Activity")


```

### Summary table

```{r, include=FALSE}

# create a summary table showing the average IMD by modality

summary_data <- data %>%
  group_by(modality) %>%
  summarize(avg_imd_rank = mean(as.numeric(imd_rank_decile), na.rm = TRUE))


```


### MSK vs Non - MSK proportion

```{r}

# create a bar chart comparing the msk vs non- msk activity

plot<- ggplot(data, aes(x = msk_flag)) +
  geom_bar(aes(y = ..prop.., group = 1), fill = "#005EB8") +
  labs(title = "Proportion of MSK vs Non-MSK Cases", x = "MSK Flag", y = "Proportion")

Presentation <- Presentation %>%
  add_slide(layout = "One Column", master = "Content Slide White")  %>%
  ph_with(value = "MSK vs Non MSK Proportion", location = ph_location_type(type = "title")) %>% 
  ph_with(value = plot, location = ph_location_label(ph_label = "Content Placeholder 2"))

```



### Boxplot imd rank deciles by modalites

```{r}
# Create a boxplot showing the IMD rank by modality


plot <- ggplot(data, aes(x = modality, y = as.numeric(imd_rank_decile))) +
  geom_boxplot(fill = "lightblue") +
  labs(title = "IMD Rank Decile by Modality", x = "Modality", y = "IMD Rank Decile")


# Add it to the slide. Use a two column slide 
Presentation <- Presentation %>%
  add_slide(layout = "Two Columns Style 1", master = "Content Slide White")  %>%
  ph_with(value = "IMD Rank and MSK", location = ph_location_type(type = "title")) %>% 
  ph_with(value = plot, location = ph_location_label(ph_label = "Content Placeholder 2"))
```


### Average IMD Rank Decile by Modality and MSK Flag

```{r}
# Create a summary table for avgerage IMD rank by modality and msk flag

summary_table <- data %>%
  group_by(modality, msk_flag) %>%
  summarize(avg_imd_rank = mean(as.numeric(imd_rank_decile), na.rm = TRUE)) %>%
  ungroup()


# Create a gt table using the summary table 
gt_table <- summary_table %>%
  gt() %>%
  tab_header(
    title = "Average IMD Rank Decile by Modality and MSK Flag",
    subtitle = "Data from 2022/23 to 2023/24"
  ) %>%
  tab_source_note(
    source_note = "Source: Your Dataset"
  ) %>%
  fmt_number(
    columns = vars(avg_imd_rank),
    decimals = 2
  ) %>%
  cols_label(
    modality = "Modality",
    msk_flag = "MSK Flag",
    avg_imd_rank = "Average IMD Rank Decile"
  )

# Add the table to the same slide as the previous one
Presentation <- Presentation %>%
  ph_with(value = plot, location = ph_location_label(ph_label = "Content Placeholder 3"))

```


### CCG Activity


```{r}
# Total activity per CCG

ggplot(data, aes(x = ccg_name)) +
  geom_bar(fill = "purple") +
  labs(title = "Activity by CCG", x = "CCG Name", y = "Activity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

# Add it to a slide. Also add some commentary


```




### Activity trend over time by modality - 2023-24

```{r}

# First, filter and aggregate the data by Year, Month, and Modality to count activities

activity_over_time <- data %>%
  filter(year == "2023/24") %>% 
  group_by(month, modality) %>%
  summarize(activity_count = n()) %>%
  ungroup()

# Plot the line chart with the date on the x-axis. Hint: you will need to use facet_wrap here

plot <- ggplot(activity_over_time, aes(x = month, y = activity_count, group = modality, color = modality)) +
  geom_smooth() +
  geom_point() +
  facet_wrap(~modality) + 
  labs(
    title = "Activity Over Time by Modality",
    x = "Date",
    y = "Number of Activities",
    color = "Modality"
  ) 

# Add the chart to a slide 
Presentation <- Presentation %>%
  add_slide(layout = "One Column", master = "Content Slide White")  %>%
  ph_with(value = "Activity Over Time by Modality", location = ph_location_type(type = "title")) %>% 
  ph_with(value = plot, location = ph_location_label(ph_label = "Content Placeholder 2"))
  
```


### Focusing on a subset - 

```{r}
# Filter data for people aged 60+, group by year and modality

filtered_data <- data %>%
  filter(age_bracket == c("61-70", "71-80", "80+")) %>%
  group_by(year, modality) %>%
  summarize(activity_count = n()) %>%
  ungroup()

# Create a summary table

gt(filtered_data) %>%
  tab_header(
    title = "Activity Summary for Ages 60+",
    subtitle = "Grouped by Year and Modality"
  )


# Add it to a slide

```



### Heatmaps with crosstabs

```{r}

#Aggregate the data by modality and msk_flag

crosstab <- data %>%
  count(modality, msk_flag)

# Plot the heatmap

plot <- ggplot(crosstab, aes(x = modality, y = msk_flag, fill = n)) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(option = "D") +
  labs(
    title = "Heatmap of Modality by MSK Flag",
    x = "Modality",
    y = "MSK Flag",
    fill = "Count"
  ) +
  theme_minimal()

# Add it to a slide

```


## Creating the ppt output


```{r}

# Create the presentation as an output

Presentation %>%
  print(target = paste0('output/PPT_workshop.pptx'))

```


## PPT Reference Layout

```{r}


layouts <- layout_summary(template_presentation)

print_placeholders <- function(layout_name, master_name){
  placeholders <- layout_properties(template_presentation, layout = layout_name, master = master_name)
  print(paste("PLaceholders:", layout_name, master_name))
  print(placeholders)
}

walk2(.x = layouts$layout, .y = layouts$master, ~print_placeholders(.x, .y))

```